---
title: "polcanR"
author: "Thierry Warin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{polcanR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(polcanR)
```

## Overview

polcanR is an R package that connects to a database containing all the tweets related to the 2021 Canadian elections between August 15, 2021 (election call) and September 20, 2021 (end of the election). [Thierry Warin](https://warin.ca) and his team powered by the [nüance-R](https://nuance-r.com) platform have collected all the tweets on this period containing one or more of the following hashtags:

- #elxn44
- #cdnpoli
- #polcan
- #ItsOurVote
- #CestNotreVote



# Practical usage

## Quick start

First, install polcanR:

```{r, eval=FALSE}
install.packages("polcanR")
```

Next, call polcanR to make sure everything is installed correctly.

```{r}
library(polcanR)
```

## How-To

### Getting the data

A user needs to enter the ISO code of a country. To have access to this code, the following function provides this information.

```{r, eval = FALSE}
polcanR::polcanr_data() # All the tweets, in all languages between August 15, 2021 (election call) and September 20, 2021 (end of the election).
polcanR::polcanr_data(dates = "2021-09-01") # All the tweets, in all languages on September 1,  2021.
polcanR::polcanr_data(languages = "en") # All the tweets in English between August 15, 2021 (election call) and September 20, 2021 (end of the election).
polcanR::polcanr_data(dates = c("2021-08-15", "2021-09-20"),languages = c("en","fr")) # All the tweets in English and French on August 15, 2021 and September 20, 2021.
```


